---
title: "Lab4"
author: "Group5 Austin Collins, Nicholas Freelove, Liuyi Bao"
date: "March 1, 2018"
output: html_document
---
Github:https://github.com/nfreelove/Lab-4
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
```

```{r}
av <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/avengers/avengers.csv", stringsAsFactors = FALSE)
head(av)
allinone <- av %>% gather(Time,Outcome, starts_with('Death'))
allinone <- allinone %>% mutate(
  Event = gsub("(.*)[1-5]","\\1",Time),
  Time = parse_number(Time))
allinone2 <- av %>% gather(Time,Outcome2, starts_with('Return'))
allinone3 <- av %>% gather(Time,DidHeReturn1,starts_with("Return1"))
allinone4 <- av %>% gather(Time,DidHeReturnAfter,one_of("Return2","Return3"))


```
## Analysis
### Total Deaths
"I counted 89 total deaths - some unlucky Avengers7 are basically Meat Loaf with an E-ZPass - and on 57 occasions the individual made a comeback. "
```{r}
count(allinone,Outcome)

```
### Total Returns
"on 57 occasions the individual made a comeback. "
```{r}
count(allinone2,Outcome2)
```
### Chance At Returning
"But you can only tempt death so many times. There's a 2-in-3 chance that a member of the Avengers returned from their first stint in the afterlife, but only a 50 percent chance they recovered from a second or third death.8"
```{r}
count(allinone3,DidHeReturn1)
count(allinone4,DidHeReturnAfter)
```

